Measuring the double-drift illusion with hand tracking

### 2021-08-07 Manuscript.Rmd
updated equations with sin and cos in latex to \sin and \cos

---
title: "Measuring the double-drift illusion with hand tracking"
author: 
- Bernard Marius 't Hart 1,*
- Denise Y.P. Henriques 1
- Patrick Cavanagh 1,2,3
output:
  word_document:
    reference_docx: template.docx
  pdf_document: default
  html_document:
    df_print: paged
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{amsmath}
bibliography: bibliography.bib
csl: journal-of-vision.csl
link-citations: yes
---

@@

We test this with a series of simple models. First, for every reset point (with coordinates $X$ and $Y$) we use the illusion strength based on a point earlier in the trajectory, expressed as either an angle (Fig. 4, left: $a = \arctan{(X/Y)}$) or a slope ($s = sin(a)/cos(a)$) to predict reset points.

@@

[3a]  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  $x = L_t \cdot v \cdot cos(a)$

[3b]  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  $y = L_t \cdot v \cdot sin(a)$

>>>>

---
title: "Measuring the double-drift illusion with hand tracking"
author: 
- Bernard Marius 't Hart 1,*
- Denise Y.P. Henriques 1
- Patrick Cavanagh 1,2,3
output:
  word_document:
    reference_docx: template.docx
  html_document:
    df_print: paged
  pdf_document: default
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{amsmath}
bibliography: bibliography.bib
csl: journal-of-vision.csl
link-citations: yes
---

@@

We test this with a series of simple models. First, for every reset point (with coordinates $X$ and $Y$) we use the illusion strength based on a point earlier in the trajectory, expressed as either an angle (Fig. 4, left: $a = \arctan{(X/Y)}$) or a slope ($s = \sin{(a)}/\cos{(a)}$) to predict reset points.

@@

[3a]  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  $x = L_t \cdot v \cdot \cos{(a)}$

[3b]  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  $y = L_t \cdot v \cdot \sin{(a)}$
